### 2022-09-18 Thesis/text/verwandt.tex
chapter 4.4 ready

\subsection{Behavior Trees}
Behavior Trees (BT) are another way to model and control the behavior of autonomous systems. Behavior Trees first found big acceptance in the computer game industry where they are mainly used to model artificial intelligence for non-player characters \cite{florez2009}. Every tree consists of one root and many child, parent and leaf nodes. Leaf nodes are also called execution nodes, while non-leaf nodes are called control or control flow nodes. 
The execution of a behavior tree is done by ticking the root node of tree. This signal then travels down to the child node of the root node, where either control nodes are being ticked or action nodes are executed. Nodes return either "Success", "Running" or "Failure" which influences how the tick signal gets processed by the rest of the behavior tree. Control nodes can be of the type "Sequence", "Fallback" or "Condition". The condition node can not have child nodes and can only return success or failure. A sequence node can be compared to a logical "and" condition. This means that once a sequence gets ticked from the parent node, it will send the tick signal to every child node as long as they return "success" of "running", and only return "success" itself when every child node was successfully ticked. If any of the child nodes return "failure", the sequence node will stop ticking the remaining children and return "failure". On the other hand the fallback node is an equivalent of a logical "or" condition. The fallback node will tick its child nodes as long as they return "failure" or "running" and will return "success" if one of the ticked node returned "success". It will only return "failure" if all of the child nodes "returned success".
Figure xx depicts an example of a BT with multiple levels and action nodes. The nodes with the arrow (->) symbol are sequence nodes, the question mark (?) symbol denotes fallback nodes. The condition node are depicted as white ovals. The action nodes are represented as gray rectangles in the BT example.

\begin{figure}
	\includegraphics[width=1.0\textwidth]{images/bt_example.jpg} 
	\caption{Example of a behavior tree \cite{iovino2022} }
\end{figure}

@@

>>>>

\subsection{Behavior Trees}
Behavior Trees (BT) are another way to model and control the behavior of autonomous systems. Behavior Trees first found big acceptance in the computer game industry where they are mainly used to model artificial intelligence for non-player characters \cite{florez2009}. Every tree consists of one root and many child, parent and leaf nodes. Leaf nodes are also called execution nodes, while non-leaf nodes are called control or control flow nodes. 
The execution of a behavior tree is done by ticking the root node of tree. This signal then travels down to the child node of the root node, where either control nodes are being ticked or action nodes are executed. Nodes return either "Success", "Running" or "Failure" which influences how the tick signal gets processed by the rest of the behavior tree. Control nodes can be of the type "Sequence", "Fallback" or "Condition". The condition node can not have child nodes and can only return success or failure. A sequence node can be compared to a logical "and" condition. This means that once a sequence gets ticked from the parent node, it will send the tick signal to every child node as long as they return "success" of "running", and only return "success" itself when every child node was successfully ticked. If any of the child nodes return "failure", the sequence node will stop ticking the remaining children and return "failure". On the other hand the fallback node is an equivalent of a logical "or" condition. The fallback node will tick its child nodes as long as they return "failure" or "running" and will return "success" if one of the ticked node returned "success". It will only return "failure" if all of the child nodes "returned success".

\begin{table}[h!]
	\caption{The five types of nodes \cite{iovino2022}}
	\begin{tabular}{ | m{0.13\textwidth} | m{0.13\textwidth}| m{0.2\textwidth} | m{0.2\textwidth} | m{0.2\textwidth} |} 
  	\hline
  	Node type & Symbol & Succeeds & Fails & Running \\ 
  	\hline
  	Sequence & - > & If all children succeed &  If one child fails & If one child returns running \\ 
  	\hline
  	Fallback & ? & If one child succeeds & If all children fail & If one child returns running \\ 
  	\hline
  	Parallel & - > - > & If >= M children succeed & If > N-M children fail & else \\
  	\hline
  	Action & shaded box & Upon completion & When impossible to complete & During completion \\
  	\hline
  	Condition & white oval & If true & If false & Never \\
  	\hline
	\end{tabular}
\end{table}

Figure xx depicts an example of a BT with multiple levels and action nodes. The nodes with the arrow (->) symbol are sequence nodes, the question mark (?) symbol denotes fallback nodes. The condition node are depicted as white ovals. The action nodes are represented as gray rectangles in the BT example.

\begin{figure}[h!]
	\includegraphics[width=1.0\textwidth]{images/bt_example.jpg} 
	\caption{Example of a behavior tree \cite{iovino2022} }
\end{figure}

@@

\subsection{POMPDs}
